Concurrent Programming in Harmony

### 2021-08-08 book/paper.tex
Added Needham/Schroeder to the book

@@

>>>>

\item \autoref{ch:ns} demonstrates finding a bug in the original Needham-Schroeder
authentication protocol.

@@

\chapter{Needham-Schroeder Authentication Protocol}
\label{ch:ns}

\begin{figure}
\begin{code}
\harmonysource{needhamschroeder}
\end{code}
\caption{\harmonylink{code/needhamschroeder.hny} Needham-Schroeder protocol and an attack.}
\label{fig:ns}
\end{figure}

The Needham-Schroeder protocol~\cite{NS78} is a security protocol in which two parties
authenticate one another by exchanging large and recently created random numbers
called \emph{nonces} that nobody else should be able to read.
The version we describe here uses \emph{public key cryptography}~\cite{pkc}: with public key
cryptography it is possible to create a message for a particular destination that
only that destination can read.  We denote with $\langle m \rangle_p$ a message
$m$ encrypted for $p$ so that only $p$ can decrypt the message and see that it contains $m$..

The original protocol goes something like this.  Suppose Alice wants to communicate
with Bob.  The three steps are as follows:

\begin{enumerate}
\item Alice creates a new nonce $N_A$ and sends $\langle 1, A, N_A \rangle_\mathtt{Bob}$
to Bob;
\item Upon receipt, Bob creates a new nonce $N_B$ and sends
$\langle 2, N_A, N_B \rangle_\mathtt{Alice}$ to Alice;
\item Alice sends $\langle 3, N_B \rangle_\mathtt{Bob}$ to Bob.
\end{enumerate}

When Bob receives $N_B$ in the last step, it decides that it is Alice that is
trying to communicate at this time.  Since it created $N_B$ recently and sent it
encrypted to Alice, Bob does not have to worry that the message was an old message
that was replayed.  Also, if Alice is honest, only Alice can have seen the message.

\autoref{fig:ns} shows the protocol implemented in Harmony.
A message $\langle m \rangle_p$ is encoded in Harmony as a dictionary
$\{ \mathtt{.dst}: p, \mathtt{.contents}: m \}$.

Unfortunately, the protocol turns out to be incorrect, but it took 17 years before
somebody noticed~\cite{Lowe95}.  The bug is easily found using model
checking~\cite{Lowe96}.
